### 2017-06-20 paper/compositional.tex
started to write sec ib compositionality

>>>>

Let $\program$ be a \PP{} of the form $\textbf{while } \Psi \textbf{ do } 
\programbody \textbf{ od}$. We denote by $\loops(\program)$ the set of all 
loops in $\program$ there are on the top level of $\programbody$, i.e. they are 
nested loops of $\program$ nested directly "below" the outer loop. We define a 
depth-1 slice of $\program$ to be a \PP{} $\slice(\program)$ obtained from 
$\program$ by removing all loops in $\loops(\program)$. A formal definition of 
both functions is given in \AppendixMaterial, we illustrate them in the 
following example.

\textbf{[PETR: INSERT EXAMPLE]}
